Replicator-mutator and noise-perturbed replicator dynamics

### 2014-09-03 snippets/square_games.Rmd
exploring square games

```{r}
a = 20
U = D
for (i in 1:4){
  for (j in 1:4){
    U[i,j] = exp(- (D[i,j]^2)/(a^2))
  }
}
show(U)
```

@@

@@

```{r}
trials = 100
rounds = 100000
break.point = 0.0000001

@@

P = matrix(0,ncol=2*ns*nm+1,nrow=trials)
colnames(P) = c("S(t1,m1)", "S(t2,m1)", "S(t3,m1)", "S(t4,m1)",
                "S(t1,m2)", "S(t2,m2)", "S(t3,m2)", "S(t4,m2)",
                "R(m1,t1)", "R(m2,t1)", "R(m1,t2)", "R(m2,t2)",
                "R(m1,t3)", "R(m2,t3)", "R(m1,t4)", "R(m2,t4)",
                "EU")

@@

  setTxtProgressBar(pb, t)

@@

    if (sum(abs(sen-s)) <= break.point & sum(abs(rec-r)) <= break.point){
      break()
    }
  }
  eu = get.eu(priors,U,sen,rec,costs)
  P[t,] = c(as.vector(c(sen, rec)),eu)
}

P = P[,c(1:8,9,11,13,15,10,12,14,16,17)]

@@

```{r}
X = round(P,4)
Y = pamk(X,krange=2:22)
show(table(Y$pamobject$clustering))
show(Y$pamobject$medoids)
```

>>>>

```{r}
a = 0.75
U = D
for (i in 1:4){
  for (j in 1:4){
    U[i,j] = exp(- (D[i,j]^2)/(a^2))
  }
}
show(U)
```

@@

Inner category coherence
------------------------

Get inner category coherence to classify results

```{r}
icc = function(D,sen,theta=0.01){
  S = sen
  S[sen>theta] = 1
  S[sen<=theta] = 0
  S = prop.table(S,2)
  out = rep(0,dim(sen)[2])
  for (i in 1:dim(sen)[2]) {
    X = rowSums(D * S[,i])
    Y = sum(S[,i] * X)
    out[i] = Y
  }
  return(sum(out))
}
```

@@

```{r}
trials = 50
rounds = 100000
break.point = 0.0000001

@@

P = matrix(0,ncol=2*ns*nm+2,nrow=trials)
colnames(P) = c("S(t1,m1)", "S(t2,m1)", "S(t3,m1)", "S(t4,m1)",
                "S(t1,m2)", "S(t2,m2)", "S(t3,m2)", "S(t4,m2)",
                "R(m1,t1)", "R(m2,t1)", "R(m1,t2)", "R(m2,t2)",
                "R(m1,t3)", "R(m2,t3)", "R(m1,t4)", "R(m2,t4)",
                "EU", "ICC")

@@

@@

    if (sum(abs(sen-s)) <= break.point & sum(abs(rec-r)) <= break.point){
      break()
    }
  }
  eu = get.eu(priors,U,sen,rec,costs)
  icc.s = icc(D,sen)
  P[t,] = c(as.vector(c(sen, rec)),eu,icc.s)
}

Q = P
# P = P[,c(1:8,9,11,13,15,10,12,14,16,17,18,19)]
P = P[,c(17,18)]

@@

```{r}
X = round(P,4)
Y = pamk(X,krange=2:15)
show(table(Y$pamobject$clustering))
show(Y$pamobject$medoids)
show(Q[Y$pamobject$id.med,1:8])
```
